---
title: "p8105_hw5_mk4022"
author: "Mary Knoop"
date: "11/4/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(dplyr)
library(purrr)
library(broom)
```

**Problem 1**  
*Part A:*  
Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. Apply this function to the columns of iris_with_missing using a map statement.

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
iris_with_missing

missing = function(x){
  if (is.numeric(x)){
    x = replace_na(x, round(mean(x, na.rm = TRUE)))
  }else if(is.character(x)) {
    x = replace_na(x, "virginica")
  }
}
filled_iris = map_df(iris_with_missing,missing)
filled_iris

```

**Problem 2**  
*Part A*  
Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time. 
```{r}
all_datafiles = list.files(path="data",full.names = T) 
all_datafiles

data = all_datafiles %>% 
  map(read_csv) %>% 
  reduce(rbind)
data

table = data %>% 
  mutate(
    id=c(1:10,1:10),
    arm=c(rep("control",10),rep("experiment",10))
)
table
```

*Part B*  
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.   
As time progresses by week, the experiemental arm values continually increase.  
```{r}
pivot_table = table %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week_num",
    values_to = "value") %>%
  ggplot(aes(x=week_num, y=value, group = id, color = arm)) + geom_point() + geom_line() +
  labs(title = "Observations over time for participants by each study arm", 
    x = "week", 
    y = "values")
pivot_table
```

**Question 3**  
*Part A*  
First set the following design elements:
* Fix n=30
* Fix xi1 as draws from a standard Normal distribution
* Fix β0=2
* Fix σ2=50
* Set β1=0
Generate 10000 datasets from the model: yi=β0+β1xi1+ϵi, with ϵi∼N[0,σ2]
For each dataset, save β̂1 and the p-value arising from a test of H:β1=0 using α=0.05
```{r}
set.seed(1)
sim_reg = function(n=30, beta0 = 2, beta1 = 0) {
  sim_data = tibble(
    x = rnorm(n, mean = 0, sd =1), 
    y = beta0 + beta1 * x +rnorm(n, 0, sqrt(50))
    )
ls_fit = lm(y ~ x, data=sim_data) %>% 
    broom::tidy()
  tibble(
    betahat_1 =ls_fit[[2,2]],
    beta1_p = ls_fit[[2,5]]
    )
}
sim_reg

sim_results = rerun(10000, sim_reg(beta1 = 0)) %>% 
  bind_rows()
sim_results
```

*Part B*  
For each dataset, save β̂1 and the p-value arising from a test of H:β1=0 using α=0.05
Repeat the above for β1={1,2,3,4,5,6}, and complete the following:

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of β2 on the x axis. Describe the association between effect size and power.
As effect size increases the power increases. 
```{r}
sim_repeat =  
  tibble(beta1_2 = c(1,2,3,4,5,6)) %>% 
  mutate(
    output_lists =  map(.x = beta1_2, ~rerun(10000, sim_reg(beta1 = .x))),
    estimate_df = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_df)

plot1 = sim_repeat %>% 
  mutate(reject_H0 = as.numeric(ifelse(beta1_p<= 0.05, "1", "0"))) %>% 
  group_by(beta1_2) %>% 
  summarize(power = mean(reject_H0)) %>% 
  ggplot(aes(x = beta1_2, y = power)) +
  geom_point() + 
  geom_line() +
  labs(
  title = "Association between effect size and power",
  x = "Value of Beta2",
  y = "Power"
  )
plot1
```
 
 *Part C*  
Make a plot showing the average estimate of β̂1 on the y axis and the true value of β1 on the x axis. Make a second plot (or overlay on the first) the average estimate of β̂1 only in samples for which the null was rejected on the y axis and the true value of β1 on the x axis. Is the sample average of β̂1 across tests for which the null is rejected approximately equal to the true value of β1? Why or why not?  

```{r}
plot2 = sim_repeat %>% 
  group_by(beta1_2) %>% 
  summarize(avg_beta1hat = mean(betahat_1)) %>% 
  ggplot(aes(x = beta1_2, y = avg_beta1hat)) +
  geom_point() + 
  geom_line() +
  labs(
  title = "True value of Beta1 vs average estimate of Beta1",
  x = "True value of Beta1",
  y = "Average estimate of Beta1"
  )
plot2

plot3 = sim_repeat %>% 
  mutate(reject_H0 = as.numeric(ifelse(beta1_p<= 0.05, "1", "0"))) %>% 
  filter(reject_H0 == 1) %>% 
  group_by(beta1_2) %>% 
  summarize(avg_beta1hat = mean(betahat_1)) %>% 
  ggplot(aes(x = beta1_2, y = avg_beta1hat)) +
  geom_point() + 
  geom_line() +
  labs(
  title = "True value of Beta1 vs average estimate of Beta1 in rejected H0 samples",
  x = "True value of Beta1",
  y = "Average estimate of Beta1"
  )
plot3
```











