---
title: "p8105_hw5_mk4022"
author: "Mary Knoop"
date: "11/4/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(dplyr)
library(purrr)
```

**Problem 1**  
*Part A:*  
Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. Apply this function to the columns of iris_with_missing using a map statement.

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
iris_with_missing

missing = function(x){
  if (is.numeric(x)){
    x = replace_na(x, round(mean(x, na.rm = TRUE)))
  }else if(is.character(x)) {
    x = replace_na(x, "virginica")
  }
}
filled_iris = map_df(iris_with_missing,missing)
filled_iris

```

**Problem 2**  
*Part A*  
Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time. 
```{r}

```

*Part B*  
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups. 







